\bfseries\LARGE\singlespacing{Transmission of respiratory viral infections with and without air cleaners in a Swiss school under non-pandemic conditions in 2023: A modeling study of epidemiological, environmental, and molecular data}

### 2023-10-17 doc/paper/manuscript-lancet.tex

There was an equal number of positive saliva samples with and without air cleaners (\cref{fig:infection-risk}b). The positivity rate remained comparable between study conditions (adjusted relative risk 0.93, 95\%-CrI 0.49 to 1.61), and was not sensitive to infection to testing delays (\supp~figure~\zref{fig:mol-estimation-results-sensitivity}).

>>>>

There was an equal number of positive saliva samples with and without air cleaners (\cref{fig:infection-risk}b). The posterior probability that fewer samples were positive with air cleaners was only 65\%. As such, the positivity rate remained comparable between study conditions (adjusted relative risk 0.93, 95\%-CrI 0.49 to 1.61), and was not sensitive to infection to testing delays (\supp~figure~\zref{fig:mol-estimation-results-sensitivity}).
